---
title: "data-download"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{data-download}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Downloading Data from the European Nucleotide Archive (ENA)

## Introduction

The European Nucleotide Archive (ENA) provides a comprehensive record of nucleotide sequence The ena_download function in our package offers a streamlined way to download data from ENA using either a query or accession numbers.

## Setup

```{r setup}
library(rena)
```

Before using the rena package, ensure you have the necessary Java runtime installed on your local machine and the ena-file-downloader.jar file in the `inst/extdata/ena-file-downloader/` directory of your package.

### Arguments

- `download_type`: A character specifying the type of download. Use ‘q’
  for query-based download or ‘a’ for accession-based download.
- `query`: A character string containing the query to retrieve specific
  data. This is required when using the ‘q’ download type.
- `accession`: A character string containing accession numbers. This is
  required when using the ‘a’ download type.
- `format`: A character string specifying the format of the data to
  download. Valid options are ‘READS_FASTQ’, ‘READS_SUBMITTED’,
  ‘ANALYSIS_SUBMITTED’, and ‘ANALYSIS_GENERATED’.
- `location`: A character string specifying the download location. By
  default, it uses the current working directory.
- `email:` A character string specifying the email address for
  notifications. By default, no email is sent.
  
Please enclose the inputs within double quotes if it contains spaces. For example, if you would like to download files in a location such as `C:\Users\Documents\ena ebi` you wuold need to delcare the location as:
```{r}
location = "`C:\Users\Documents\ena ebi`"
```


## Download data using a query

```{r}
rena::ena_download("a", accession = "SAMEA3231268,SAMEA3231287", format = "READS_FASTQ", location = "C:/Users/ns651/OneDrive")
```

## Download data using accession numbers

```{r}
ena_download("a", accession = "SAMEA3231268,SAMEA3231287", format = "READS_FASTQ")
```

Files downloaded using this function are saved to the specified location provided as an argument. If no location is specified, files will default to the current working directory. Additionally, each execution of the download command generates an update to a log file in your `logs` folder in your local directory. This log captures details of the build process and can be invaluable for troubleshooting in the event of any issues or errors during the download.
