---
title: "Xref"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{xref}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Xref

The ENA Xref service holds cross-references to a number of external data resources linked to ENA records. These cross-reference sources include both services operated by colleagues at EMBL-EBI (such as UniProt and Ensembl) as well as those operated outside EMBL-EBI (including SILVA and RFAM).

These can be searched across and explored using the cross-reference search. You can navigate to the cross-reference search here:

https://www.ebi.ac.uk/ena/browser/xref


There are four functionalities of the cross-reference search:

- Search Active DB's

- Search Target 

- Search Count

- Full Search

These functionalites work as follows:

If one would like to search the active repositories in the xref system one would need to run:

```{r, eval = FALSE}
library(rena)
xref_active()
```

This will return a dataframe with the active Xref Databases and their respective descriptions.

Following this, if one would like to know the types of target data available in a database they can search:

```{r, eval = FALSE}
xref_target("ArrayExpress")
```


